### 2022-03-04 README.Rmd
updated docs, added c4a_ls

# Colors for all!

@@

![categorical palettes)](https://user-images.githubusercontent.com/2444081/155185594-a52c361f-7113-40fe-82ea-94e782c27be4.png)
![sequential palettes)](https://user-images.githubusercontent.com/2444081/155185615-9356443d-8a18-40a6-bc9e-d2e0d8e26eb4.png)
![diverging palettes)](https://user-images.githubusercontent.com/2444081/155185638-3d05a045-c794-4eab-b994-88c0b58196e2.png)

@@

```{r}
getwd()
devtools::load_all(".")
```

## Get started

Navigation through the color palettes is easy via the gui shown above, which is started with:

@@

@@

>>>>

# Colors for all! <img src='inst/img/cols4all_logo.png' align="right" height="139" />

@@

Categorical             |  Sequential | Diverging
:-------------------------:|:-------------------------:|:-------------------------:
[![](https://user-images.githubusercontent.com/2444081/156847689-7e1a4608-9b03-45f5-9ccf-56e6d8844d47.png)](https://user-images.githubusercontent.com/2444081/156847689-7e1a4608-9b03-45f5-9ccf-56e6d8844d47.png) | [![](https://user-images.githubusercontent.com/2444081/156847703-b429c521-89d5-4e14-85c1-0f100ca93b45.png)](https://user-images.githubusercontent.com/2444081/156847703-b429c521-89d5-4e14-85c1-0f100ca93b45.png) | [![](https://user-images.githubusercontent.com/2444081/156847712-33a3cd22-a50b-44e2-9666-b67fcb0d2853.png)]((https://user-images.githubusercontent.com/2444081/156847712-33a3cd22-a50b-44e2-9666-b67fcb0d2853.png))

@@

```{r, echo=FALSE}
getwd()
devtools::load_all(".")
```

## Getting started

Navigation through the color palettes is easy via the GUI shown above, which is started with:

@@

Besides browsing through palettes, it is also easy to copy color codes to the clipboard, either by selecting the hidden text in the color tables or by clicking on the icons at the right-hand-side:

![](https://user-images.githubusercontent.com/2444081/156849917-59af1dc1-ee5e-40be-bf87-5c7384351ae0.png){width=50%}

@@

## Overview of functions

Main functions:

* `c4a_gui` GUI (shiny app) to see and analyse the palettes
* `c4a` Get the colors of a palette

Palette names and properties:

* `c4a_palettes` Get available palette names
* `c4a_series` Get available series
* `c4a_meta` Get meta information (such as type and maximum number of colors )
* `c4a_ls` Environment via which palette names can be browsed with auto-completion (using `$`)

Importing and exporting palettes:

* `c4a_series_add` Add color palettes
* `c4a_series_remove` Remove color palettes
* `c4a_sysdata_import` Import system data
* `c4a_sysdata_export` Export system data

ggplot2

* `scale_<aesthetic>_<mapping>_c4a_<type>` e.g. `scale_color_continuous_c4a_div` Add scale to ggplot2.
